---
title: |
    | Summary Report for the
    | Ministry of `r id`
author: "BC Stats"
output:
  pdf_document: default

---



```{r setup, include=FALSE, message= FALSE }
knitr::opts_chunk$set(echo = TRUE)

```

\centering

\includegraphics{data/BCStats.png}

\raggedright
\clearpage
\tableofcontents

\newpage

## Executive Summary

### Engagement States

The Ministry of `r id` had `r dataset %>% dplyr::filter(ORGID15 == id) %>% nrow()` employees in 2015. According to the survey, there were `r dataset %>% dplyr::filter(ORGID15 == id & ENG_STATE_15 == "Engaged") %>% nrow()` engaged employees in the ministry, while `r dataset %>% dplyr::filter(ORGID15 == id & ENG_STATE_15 == "Disengaged") %>% nrow()` employees were disengaged. 


```{r Figure 1, echo= FALSE, message= FALSE }
ggplot(data = dataset %>% dplyr::filter(ORGID15 == id), aes(x=ENG_STATE_15)) +
  ggtitle("Figure 1: Distribution of Engagement States") +
  geom_bar(stat="count", fill="DarkGreen") +
  theme_classic() +
  theme(panel.grid.minor = element_blank(),
          axis.line = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.x = element_text(angle = 25, vjust = 0.75))
    
  
  
```

\newpage

### Commitment and Job Satisfaction

In 2015, the Ministry of `r id` had an average commitment score of `r dataset %>% dplyr::filter(ORGID15 == id & !is.na(Commitment_15)) %>% summarise(avg = mean(Commitment_15))` and an average job satisfaction score of `r dataset %>% dplyr::filter(ORGID15 == id & !is.na(Job_Satisfaction_15)) %>% summarise(avg = mean(Job_Satisfaction_15))`. 

The average commitment scores varied for individuals across different engagement states.

```{r Figure 2, echo= FALSE, message= FALSE }
ggplot(data = dataset %>% dplyr::filter(ORGID15 == id & !is.na(Commitment_15) & !is.na(Job_Satisfaction_15)),
       aes(ENG_STATE_15)) +
  ggtitle("Figure 2: Commitment Across Engagement States") +
  stat_summary_bin(aes(y = Commitment_15), fun.y = "mean", geom = "bar", fill = "darkblue") +
  theme_classic() +
  theme(panel.grid.minor = element_blank(),
          axis.line = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.x = element_text(angle = 25, vjust = 0.75))
    
  
  
```

In addition, the average job satisfaction scores varied for individuals across different engagement states as well

```{r Figure 3, echo= FALSE, message= FALSE }
ggplot(data = dataset %>% dplyr::filter(ORGID15 == id & !is.na(Commitment_15) & !is.na(Job_Satisfaction_15)),
       aes(ENG_STATE_15)) +
  ggtitle("Figure 3: Job Satisfaction Across Engagement States") +
  stat_summary_bin(aes(y = Job_Satisfaction_15), fun.y = "mean", geom = "bar", fill = "lightblue") +
  theme_classic() +
  theme(panel.grid.minor = element_blank(),
          axis.line = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.x = element_text(angle = 25, vjust = 0.75))

  
  
```
